\chapter*{Publications et manuscrit}

\begin{itemize}
\item Thariat J, \textbf{Azzopardi N}, Peyrade F, Launay-Vacher V, Santini J, Lecomte T, Etienne-Grimaldi M-C, Paintaud G, Milano G.\\
\textit{Cetuximab pharmacokinetics in end-stage kidney disease under hemodialysis.}\\
Journal of Clinical Oncology. 2008 ; 26(25) : 4223-5.
\\
\item Cézé N, Ternant D, Piller F, Degenne D, \textbf{Azzopardi N}, Dorval E, Watier H, Lecomte T, Paintaud G.\\
\textit{An enzyme-linked immunosorbent assay for therapeutic drug monitoring of cetuximab.}\\
Therapeutic Drug Monitoring. 2009 ; 31(5) : 597-601.
\\
\item \textbf{Azzopardi N}, Lecomte T, Ternant D, Boisdron-Celle M, Piller F, Morel A, Gouilleux-Gruart V, Vignault-Desvignes C, Watier H, Gamelin E, Paintaud G.\\
\textit{Cetuximab pharmacokinetics influences progression-free survival of metastatic colorectal cancer patients.}\\
Clinical Cancer Research. 2011 ; 17(19) : 1-9.
\\
\item \textbf{Azzopardi N}, Pointreau Y, Ternant D, Paintaud G, Lecomte T.\\
\textit{Influence of infusion intervals on cetuximab concentrations: a simulation study.}\\
Manuscrit.
\\
\item Maillet A, Guilleminault L, Lemarié E, Lerondel S, \textbf{Azzopardi N}, Montharu J, Congy-Jolivet N, Reverdiau P, Legrain B, Parent C, Douvin D-H, Hureaux J, Courty Y, de Monte M, Diot P, Paintaud G, Le Pape A, Watier H, Heuzé-Vourc'h N.\\
\textit{The airways, a novel route for delivering monoclonal antibodies to treat lung tumors.}\\
Pharmaceutical Research. 2011 ; 28(9) : 2147-56.
\end{itemize}